A Multi-Modal Model for Prediction and Classification of Object Deformation during Robotic Manipulation

### 2016-08-25 AnswersToComments.tex
Corrected collision detection

\comment{There is an omission here: the article aims at predicting the force and deformation on the visual plane of the three-dimensional object.  The tracking of the shape is used only during training and for evaluation purposes.}

@@

@@

18, in section V-A, please explain why evolutionary algorithm is used. In algorithm 4, please explain what $\alpha, \beta,\gamma,\zeta$ represent.

@@

>>>>

\comment{It is important to make a precision here: the article aims at predicting the force and deformation on the visual plane of the three-dimensional object.  The tracking of the shape is used only during training as part of the evaluation function.}

@@

\comment{Improved the description across the whole subsection.}

@@

\comment{No, that is why we mentioned in the text that it is a common algorithm.  It can be found across the web in many sites.  Should we mention something about that in the caption?}

18, in section V-A, please explain why evolutionary algorithm is used. In algorithm 4, please explain what $\alpha, \beta, \gamma, \zeta$ represent.

@@

\comment{We don't focus on tracking, we want to predict several frames ahead, not follow, that is why closely related works are few.}

### 2016-08-25 twostagedo.tex
Corrected collision detection

\subsection{Collision Detection}
In the scenario, rigid objects are treated as geometric obstacles.  Two types of obstacles are considered: circles and a floor line that can not be crossed.  For the floor obstacle, the collision is roughly solved by pushing vertices back to the border of the floor.  The springs will eventually propagate the effect to the neighbours.  For the circle the resolution is in two stages: vertices and edges.  A vertex will be pushed out to a distance $\epsilon$ of the finger, in the direction of the radius.  For edges, the common algorithm in \alref{alg:point_segment} is used to estimate the shortest distance between the centre of the circle and the edge.  Given this distance, the algorithm in \alref{alg:push_edge} indicates how and in which direction the edge must be displaced.

>>>>

\subsection{Collision Detection}
In the scenario, rigid objects \comment{(like the robotic finger and the table)} are treated as geometric obstacles.  \comment{When the simulation of the behaviour of the mesh, that models the image of the sponge, is carried on, the predicted positions of the vertices may indicate that the mesh penetrates the obstacles.  This should be interpreted as a collision between the sponge and the obstacle.  Since the sponge can not penetrate an obstacle, the overlapping between geometries must be solved, and its physical consequences must affect the simulation.  For example: if vertices of the mesh overlap the table, the sponge will remain on top of the table, with its material being more compact, which will cause the response force propagated towards the finger to be increased.

In order to model this,} two types of \comment{solid} obstacles are considered: circles \comment{(for the finger)} and a table line that can not be crossed.  For the table obstacle, the collision \comment{of parts of the sponge with it} is roughly solved by pushing vertices \comment{of the mesh of the sponge} back to the border of the table.  The springs will eventually propagate the effect to the neighbours.  For the circle the resolution is in two stages: vertices and edges.  A vertex will be pushed out to a distance $\epsilon$ of the finger, in the direction of the radius.  For edges, the common algorithm in \alref{alg:point_segment} is used to estimate the shortest distance between the centre of the circle and the edge.  Given this distance, the algorithm in \alref{alg:push_edge} indicates how and in which direction the edge must be displaced.
